Goals and Tasks

### 2020-05-12 README.Rmd
small change to readme

## Location Scale Regression Boost Model

>>>>

## Working with Location Scale Regression Boost Model
First, you need to install the `asp20model` &  `asp20boost` package from GitLab and load it:

```{r installation, eval = 3}
install.packages("devtools")
#This throws an error for asp20boost
#devtools::install_gitlab("asp20/asp20model", host = "gitlab.gwdg.de")
#devtools::install_gitlab("asp20/asp20boost", host = "gitlab.gwdg.de")
